The population of long-period transiting exoplanets \vspace{-3\baselineskip}

### 2016-07-16 document/ms.tex
Adding @davidwhogg's words becuase he's bad at git

% Projects:
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\kepler}{\project{Kepler}}
\newcommand{\KT}{\project{K2}}
\newcommand{\tess}{\project{TESS}}
\newcommand{\plato}{\project{PLATO}}
\newcommand{\pdc}{\project{PDC}}
\newcommand{\bls}{\project{BLS}}
\newcommand{\emcee}{\project{emcee}}
\newcommand{\exosyspop}{\project{exosyspop}}

@@

>>>>

% Projects:
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\kepler}{\project{Kepler}}
\newcommand{\KT}{\project{K2}}
\newcommand{\tess}{\project{TESS}}
\newcommand{\plato}{\project{PLATO}}
\newcommand{\gaia}{\project{Gaia}}
\newcommand{\pdc}{\project{PDC}}
\newcommand{\bls}{\project{BLS}}
\newcommand{\emcee}{\project{emcee}}
\newcommand{\exosyspop}{\project{exosyspop}}

@@

In priniciple the \gaia\ Mission will be very sensitive to the astrometric
wobble produced by a long-period exoplanet \citep{Perryman:2014}.
To leading order, the astrometric signal strength is proportional to the
semi-major axis of the stellar (primary) reflex motion in angular units.
That is, detectability is related to the angle $\alpha$ given by
\begin{eqnarray}
alpha &=& \frac{a}{D}\,\frac{M_{\mathrm p}}{M_{\mathrm s}} \quad ,
\end{eqnarray}
% obviously fix to your notation!
where $a$ is the semi-major axis, $D$ is the distance from the observer to the
primary, and $M_{\mathrm{p}}/M_{\mathrm{s}}$ is the planet-to-star mass ratio.

The single-visit precision of \gaia\ will vary with magnitude but is expected
to be on the order of 40\,$\mu$as at these magnitudes \hoggtodo{cite
something}.
In detail the confidence with which an exoplanet can be detected or measured
in the final \gaia\ data depends on this precision, the number of crossings of
the star through the \gaia\ focal plane, and details of how the projected
orbit is sampled by the time history of the focal-plane crossings.
However, it is not expected that \gaia\ can detect or measure precisely
exoplanet-induced astrometric wobbles that are much smaller in amplitude than
the single-visit precision \citep{Perryman:2014}.

The primary stars in the \kepler\  Field are typically at distances of $\sim
500$\,pc, and typical mass ratios are in the $10^{-4}$ range.
We therefore expect astrometric amplitudes in the 0.3 to 3\,$\mu$as range.
These planets will not be detectable or measurable in the \gaia\ data under
any circumstances.
However, similar planets around closer stars \emph{will} be detectable with
\gaia.
This means that there will be a comparable exoplanet occurrence rate
measurement from the \gaia\ data.
It also means that many of the discoveries of the \tess\ Mission will be
followed up and precisely measured by the \gaia\ Mission.
